Supplement: A Continuous Occlusion Model for Road Scene Understanding

### 2016-04-08 CVPR16/Source/related.tex
Camera ready version

\vspace{-0.3cm}
\paragraph{Motion segmentation and multibody SFM}
An application for our occlusion modeling is to determine point track associations in scenes with multiple objects. For moving objects, this is within the purview of motion segmentation, which has been approached through algebraic factorization methods \cite{Costeria98,Vidal03,Vidal04}, statistical methods~\cite{Kanatani01,Gruber04,Rao08} and clustering methods~\cite{Yan06,Goh07}. Some recent efforts include robust algebraic segmentation with hybrid perspective constraints \cite{Rao_etal_2010} and spectral clustering with point track spatial affinities \cite{Brox_Malik_2010}. Unlike our work, such methods cannot handle static objects, or dynamic objects with little relative motion.
%\cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. 
Closer to our application, motion segmentation is also used within multibody SFM frameworks \cite{Ozden_etal_2010,Kundu_etal_2011,Namdev2012}. In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.

@@

\vspace{-0.3cm}
\paragraph{3D localization}
One of the vital goals of 3D scene understanding is to localize the 3D objects in complex scenes. 
%For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology. 
Monocular frameworks like ours have also reasoned about occlusions, for instance, \cite{Wojek_etal_2013} considers partial object detectors. A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014,Zia2015}, which also allows reasoning about mutual occlusions between objects. In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space and derives unified representations for SFM points and object detection bounding boxes. This makes our model more general, extensible and amenable for continuous optimization.

>>>>

\vspace{-0.3cm}
\paragraph{Motion segmentation and multibody SFM}
An application for our occlusion modeling is to determine point track associations in scenes with multiple objects. For moving objects, this is within the purview of motion segmentation, which has been approached through algebraic factorization methods \cite{Costeria98,Vidal03,Vidal04}, statistical methods~\cite{Kanatani01,Gruber04,Rao08} and clustering methods~\cite{Yan06,Goh07}. Some recent efforts include robust algebraic segmentation with hybrid perspective constraints \cite{Rao_etal_2010} and spectral clustering with point track spatial affinities \cite{Brox_Malik_2010}. Unlike our work, such methods cannot handle static objects, or dynamic objects with little relative motion.
%\cite{Tron_Vidal_2007,Rao_etal_2010}. This also motivates further applications such as object segmentation based on point trajectories \cite{Brox_Malik_2010}. 
Closer to our application, motion segmentation is also used within multibody SFM frameworks \cite{Kundu_etal_2011,Namdev2012,Ozden_etal_2010}. In contrast to these works, our formulation does not distinguish between moving and static objects and also explicitly reasons about occlusions due to 3D object geometries for associating point tracks to individual objects.

@@

\vspace{-0.3cm}
\paragraph{3D localization}
One of the vital goals of 3D scene understanding is to localize 3D objects in complex scenes. 
%For instance, using stereo imagery, several visual cues are combined in \cite{Geiger_etal_2014} to simultaneously determine object locations and a rough intersection topology. 
Monocular frameworks like ours have also reasoned about occlusions, for instance, partial object detectors are considered in \cite{Wojek_etal_2013}. A detailed part-based representation of objects based on annotated CAD models is used for monocular scene understanding in \cite{Zia_etal_2013,Zia_etal_2014,Zia2015}, which also allows reasoning about mutual occlusions between objects. In contrast to these works, our monocular framework uses a physical modeling of occlusion in continuous space and derives unified representations for SFM points and object detection bounding boxes. This makes our model more general, extensible and amenable for continuous optimization.

### 2016-04-08 CVPR16/supplementarymaterial.tex
update Supp
Camera ready version

%\cvprfinalcopy % *** Uncomment this line for the final submission

@@

\author{Vikas Dhiman\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small dhiman@umich.edu}
Quoc-Huy Tran\\
NEC Laboratories America, Inc.\\
Cupertino, CA, USA\\
{\tt\small qhtran@nec-labs.com}
\and
Manmohan Chandraker\\
NEC Laboratories America, Inc.\\
Cupertino, CA, USA\\
{\tt\small manu@nec-labs.com}
\and
Jason J Corso\\
  University of Michigan\\
  Ann Arbor, MI, USA\\
{\tt\small jjcorso@eecs.umich.edu}
}

@@

>>>>

\cvprfinalcopy % *** Uncomment this line for the final submission

@@

\author{Vikas Dhiman$^\dagger$
\and
Quoc-Huy Tran$^*$
\and
Jason J. Corso$^\dagger$
\and
Manmohan Chandraker$^*$
\and
$^\dagger$ University of Michigan,\\
Ann Arbor, MI, USA
%{\tt\small \{dhiman,jjcorso\}@umich.edu}
\and
$^*$ NEC Laboratories America, Inc.\\
Cupertino, CA, USA
%{\tt\small \{qhtran,manu\}@nec-labs.com}
}

@@

\section{Parameters value used}
\begin{table}[!h]
  \centering
\begin{tabular}{cccccc}
  \toprule
  Parameters
  & $\lambda_{\text{track}}$  
  & $\lambda_{\text{detect}}$ 
  & $\lambda_{\text{dyn}}$    
  & $\lambda_{\text{size}}$   
  & $k_u$, $k_d$ \\
  \midrule
  Value
  & 1
  & 1
  & 10
  & 7
  & $10\ln(49)$\\
  \bottomrule
\end{tabular}
\caption{Parameter values used for experiments}
\label{tab:paramters}
\end{table}
